### 2019-01-19 thesis/2_chapters/chap2.tex
Fix all typos

% Chapter 2
\chapter{Literature preview}
\label{chap:lit_review}

@@

The star tracking algorithm operates mainly in 2 different modes: the Lost in Space (LIS) and Tracking modes:
\begin{itemize}
	\item LIS mode: the initial attitude is unknown, the star tracker must determine it which is the most critical part of the star tracking operation. LIS mode is operated at the time when the power system on or resets after an attitude determination attempt from tracking mode failed\cite{edselc.2-52.0-8487677997120120101}.
	\item Tracking mode: after the initial attitude is recognized. The star tracker is switched to the Tracking mode. With the initial is acknowledged, the computing can easily predict and track the attitude based on the previous information.
\end{itemize}

\noindent On this research topic, we will only focus on the LIS mode operation. The LIS mode operation of a star tracker is generalize in Figure~\ref{fig:2_1} included in 3 main algorithms:
\begin{itemize}
	\item Centroiding Algorithm: Perform an image preprocessing, the input is a star image captured from the image sensor processed to an output which are the coordinates of all star clusters presented in the image.
	\item Star Recognition Algorithm: The main part of LIS mode. The coordinates of the stars will be used to calculate a feature vector depending on a specific Star Algorithm. A Star Pattern Database (SPD) is also prebuilt from the SAO catalog (Smithsonian Astrophysical Observatory Star Catalog) based on the specific pattern of the Star Algorithm and stored into the memory of the processing system for comparison and pattern recognition\cite{edseee.655799920130101}. Then, the feature vector will be looked up and matched to an entry in the SPD. The entry will return a star ID which is an identification of a star presenting in the star image.
	\item Attitude Determination stage: The final stage of star tracking algorithm operated in LIS mode. The Star ID will be looked up again in the SAO catalog to extract the information about its attitude. Then a group of star attitude is still used to calculate the attitude of the satellite. Some of the well-known Attitude Determination methods are the QUEST and TRIAD.
\end{itemize}

@@

The first step is to acquire the image which is accomplished by the image sensor. The image acquired has to be processed for estimating the coordinate of the stars in the image plane. This is completed by applying the centroiding process on the image. The input of this step is a star image with multiple star clusters, the output is the coordinates of every stars presenting. Due to distributed energy surface, a star projection is spread over a 3x3 to 11x11 square area\cite{ntu.54658220060101}, the star projection is a group of connected pixels. Therefore, the best way to identify the star clusters is to apply the ‘connected component’ algorithm.

@@

% Table 2.1
\noindent Table~\ref{tab:starList}. \\

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Section 2.3
\section{Liebe Star Recognition algorithm}

@@

% Equation 2.2
\noindent The star triplet will form 2 angular distance $\theta_1, \theta_2$ and 1 angular angle $\theta$ which are defined by Equation~\ref{eq:2_2}
\begin{equation}
	\begin{aligned}
		\theta_1 = \cos(V_A, V_B) \\
		\theta_2 = \cos(V_A, V_C) \\
		\theta = \cos(V_{AB}, V_{AC})
	\end{aligned}
	\label{eq:2_2}
\end{equation}

@@

\noindent The weakness of this algorithm is the weak robustness due to the limitation of star utilizing. It only employs the three nearest stars to the centre and discards other stars which will then lead to a mismatch if the 2 predefined nearest neighboring star does not appear in the star image. Besides, if the reference star appears in the final entry of the Star Pattern Database.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Section 2.4
\section{Pyramid star recognition algorithm}

@@

\noindent Moreover, the pyramid star recognition algorithm has not yet solved the mismatch problem caused by missing stars. In the case of one or more neighboring stars of the reference, the star is missing the algorithm will fail and do not produce a correct result. \\

@@

To overcome the weakness of Liebe and Pyramid star recognition algorithm, the Geometric Voting is proposed based on voting of radial distances\cite{edseee.456019820080101}. The Geometric Voting method considers all the nearby stars of the reference star appeared in the star image. Thanks to all stars in the image are employed, the Pyramid algorithm becomes more robust than the first two algorithms.

@@

\noindent After capturing the image, $r_1, r_2,…,r_n$ are calculated based on the distance from the closest star to the centre which is the reference star to all other stars within the FOV of the star sensor. Then all the distances from the feature vector are compared to the predefined neighboring distances of every star ID in the SPD. With each distance is matched, a voting value of the star ID is increased. After the comparing distance stage processed, the star ID which has the highest vote is recognized as the correct star ID candidate. \\

\noindent For the advantage of this recognition method, firstly it employs all the data presenting in the image. As a result, it reduces the mismatching issued caused by lack of data proposed by Liebe and Pyramid method. Thus, it is the most robust star recognition method compared to the first two introduced methods. \\

\noindent The critical drawback of this method is the enormous space complexity needed to store the Star Pattern Database since each star ID entry must store the information of all of its neighboring stars. It leads to a requirement that a large memory must be used to store the Star Pattern Database to trade off the accuracy and robustness. Thus, the processing time for returning a star ID is increasing due to the increase in data processing and comparisons through the whole database.

@@

In a quick review and analysis of the 3 prestigious and famous star recognition, we can come up with a conclusion that there is a trade-off between accuracy and robustness with the space complexity and processing time required. For the star tracker system, the choice of algorithm to be implemented on will depend on the scale of the satellite project. For military satellite, we favor the accuracy and robustness over the complexity of time and space. Thus, the computer system on those satellites must be fast enough to handle the complexity. \\

\noindent For the implementation on the nanosatellites, the computer system is a small embedded processor with limited memory and processing ability which can not handle a large number of computations. Therefore, we need an optimized algorithm that is accurate, robust and can be implemented on a concise computer system. \\

\noindent The chosen star tracking algorithm is conducted by the research “An Autonomous Star Recognition Algorithm with Optimized Star Catalogue for Fast Search Performance” M.D. Pham, K.S. Low and S.H. Chen\cite{edselc.2-52.0-8487677997120120101,edseee.655799920130101}. The research introduces a novel star pattern identification using an optimized database and proposes a search tree data structure for quick and advanced parallel search. \\

@@

\noindent The feature vector is described in Figure~\ref{fig:2_8}.
\begin{center}
	\begin{itemize}
		\item N: Number of stars appeared within the FOV of the star sensor.
		\item $D_1, D_2, D_3…, D_n$: Distance from the reference star to all of its neighbors.
	\end{itemize}
\end{center}

\noindent To search and match the star pattern vector with the database, a special database structure is pre-built. The tree is built with multiple levels, the first level is N-Number of stars in the FOV, next layers will be the distances from the reference stars to all of its neighbors which are sorted ascendingly from nearest neighboring star to the farthest. \\

\noindent In the searching and matching stage, each parameter from the star pattern is dispatched and matched to the equivalent level. If the matching succeeds, the next layer is considered. If all layers are matched the correct star ID will be returned; otherwise, we return a statement that the star pattern is a false pattern, no stars were matched. In this case, depend on the attitude determination system on the satellite, the star identification algorithm would be rerun or skipped to proceed the next star image.

>>>>

% Chapter 2
\chapter{Literature Review}
\label{chap:lit_review}

@@

The star tracking algorithm operates mainly in 2 different modes: the Lost in Space (LIS) and Tracking modes:
\begin{itemize}
	\item LIS mode: the initial attitude is unknown, the star tracker must determine it which is the most critical part of the star tracking operation. LIS mode is operated at the time when the power system is switched on or reset after an attitude determination attempt from tracking mode failed\cite{edselc.2-52.0-8487677997120120101}.
	\item Tracking mode: after the initial attitude is recognized. The star tracker is switched to the Tracking mode. With the initial is acknowledged, the computing can easily predict and track the attitude based on the previous information.
\end{itemize}

\noindent On this research topic, we will only focus on the LIS mode operation. The LIS mode operation of a star tracker is generalized in Figure~\ref{fig:2_1} which includes 3 main algorithms:
\begin{itemize}
	\item Centroiding Algorithm: Perform an image preprocessing, the input is a star image captured from the image sensor processed to an output which are the coordinates of all star clusters presented in the image.
	\item Star Recognition Algorithm: The main part of LIS mode. The coordinates of the stars will be used to calculate a feature vector depending on a specific Star Algorithm. A Star Pattern Database (SPD) is also prebuilt from the SAO catalog (Smithsonian Astrophysical Observatory Star Catalog) based on the specific pattern of the Star Algorithm and stored into the memory of the processing system for comparison and pattern recognition\cite{edseee.655799920130101}. Then, the feature vector will be looked up and matched to an entry in the SPD. The entry will return a star ID which is an identification of a star presenting in the star image.
	\item Attitude Determination stage: The final stage of star tracking algorithm operated in LIS mode. The Star ID will be looked up again in the SAO catalog to extract the information about its attitude. Then a group of star attitude is used to calculate the attitude of the satellite. Some of the well-known Attitude Determination methods are the QUEST and TRIAD.
\end{itemize}

@@

The first step is to acquire the image which is accomplished by the image sensor. The image acquired has to be processed for estimating the coordinates of the stars in the image plane. This is completed by applying the centroiding process on the image. The input of this step is a star image with multiple star clusters. The output is the coordinate of every star presenting. Due to distributed energy surface, a star projection is spread over a 3x3 to 11x11 square area\cite{ntu.54658220060101}, the star projection is a group of connected pixels. Therefore, the best way to identify the star clusters is to apply the ‘connected component’ algorithm.

@@

% Table 2.1
\noindent Table~\ref{tab:starList} .\\

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Section 2.3
\section{Liebe Star Recognition Algorithm}

@@

% Equation 2.2
\noindent The star triplet will form 2 angular distances $\theta_1, \theta_2$ and 1 angular angle $\theta$ which are defined by Equation~\ref{eq:2_2}
\begin{equation}
	\begin{aligned}
		\theta_1 = \cos(V_A, V_B) \\
		\theta_2 = \cos(V_A, V_C) \\
		\theta = \cos(V_{AB}, V_{AC})
	\end{aligned}
	\label{eq:2_2}
\end{equation}

@@

\noindent The weakness of this algorithm is the weak robustness due to the limitation of star utilization. It only employs the three nearest stars to the centre and discards other stars which will then lead to a mismatch if the 2 predefined nearest neighboring stars does not appear in the star image. Besides, if the reference star appears in the final entry of the Star Pattern Database.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Section 2.4
\section{Pyramid Star Recognition Algorithm}

@@

\noindent Moreover, the pyramid star recognition algorithm has not yet solved the mismatch problem caused by missing stars. In the case of one or more neighboring stars of the reference are missing, the algorithm will fail and do not produce a correct result. \\

@@

To overcome the weaknesses of Liebe and Pyramid star recognition algorithms, the Geometric Voting is proposed based on voting of radial distances\cite{edseee.456019820080101}. The Geometric Voting method considers all the nearby stars of the reference star appeared in the star image. Thanks to all stars in the image are employed, the Pyramid algorithm becomes more robust than the first two algorithms.

@@

\noindent After capturing the image, $r_1, r_2,...,r_n$ are calculated based on the distance from the closest star to the centre which is the reference star for all other stars within the Field of View(FOV) of the star sensor. Then all the distances from the feature vector are compared to the predefined neighboring distances of every star ID in the SPD. With each distance is matched, a voting value of the star ID is increased. After the comparing distance stage processed, the star ID which has the highest vote is recognized as the correct star ID candidate. \\

\noindent The advantage of this recognition method is that it employs all the data presenting in the image. As a result, it reduces the mismatching issued caused by lack of data proposed by Liebe and Pyramid method. Thus, it is the most robust star recognition method compared to the first two introduced methods. \\

\noindent The critical drawback of this method is the enormous space complexity needed to store the Star Pattern Database since each star ID entry must store the information of all of its neighboring stars. It leads to the requirement that a large memory must be used to store the Star Pattern Database to trade off of the accuracy and robustness. Thus, the processing time for returning a star ID is increasing due to the increase in data processing and comparisons through the whole database.

@@

In a quick review and analysis of the 3 prestigious and famous star recognition algorithms, we can come up with a conclusion that there is a trade-off between accuracy and robustness with the space complexity and processing time required. For the star tracker system, the choice of algorithm to be implemented on will depend on the scale of the satellite project. For military satellite, we favor the accuracy and robustness over the complexity of time and space. Thus, the computer system on those satellites must be fast enough to handle the complexity. \\

\noindent For the implementation on the nanosatellites, the computer system is a small embedded processor with limited memory and processing ability which can not handle a large number of computations. Therefore, we need an optimized algorithm that is accurate, robust and can be implemented on a small computer system. \\

\noindent The chosen star tracking algorithm is from the paper “An Autonomous Star Recognition Algorithm with Optimized Star Catalogue for Fast Search Performance” by M.D. Pham, K.S. Low and S.H. Chen\cite{edselc.2-52.0-8487677997120120101,edseee.655799920130101}. The algorithm introduces a novel star pattern identification using an optimized database and proposes a search tree data structure for quick and advanced parallel search. \\

@@

\noindent The feature vector is described in Figure~\ref{fig:2_8}.
\begin{center}
	\begin{itemize}
		\item N: Number of stars appeared within the FOV of the star sensor.
		\item $D_1, D_2, D_3, ..., D_n$: Distances from the reference star to all of its neighbors.
	\end{itemize}
\end{center}

\noindent To search and match the star pattern vector with the database, a special database structure is pre-built. The tree structure is built with multiple levels, the first level is N-Number of stars in the FOV, next layers will be the distances from the reference stars to all of its neighbors which are sorted ascendingly from nearest neighboring star to the farthest. \\

\noindent In the searching and matching stage, each parameter from the star pattern is dispatched and matched to the equivalent level. If the matching succeeds, the next layer is considered. If all layers are matched the correct star ID will be returned; otherwise, we return a statement that the star pattern is a false pattern, no stars were matched. In this case, depend on the attitude determination system on the satellite, the star identification algorithm would be rerun or skipped to proceed to the next star image.

### 2019-01-19 thesis/2_chapters/chap3.tex
Fix all typos

\noindent \textbf{FPGA design flow}: The design begins with design entry, continues with simulation to verify the logic is implemented as expected, and then the tool will perform synthesis (also called mapping) to map the logic to the device architecture. Next the tool will create the interconnection between cells by place and routing (or fitting) the design. Another simulation after the fitting is done is a good practice. If this looks good, the next step to use the tool to create a programming file, which is then downloaded into the FPGA device for testing\cite{Coursera}. \\

@@

\noindent Traditional SoC board is a fixed Application Specific Integrated Circuit (ASIC) with is prebuilt for only one particular function or task. The processing time of ASIC board is speedy and high-efficiency due to the unique hardware prebuilt for this task. In the trade-off, the development time of an ASIC board takes much time due to multiple stages of hardware synthesis, testing and verification and the cost of development is enormous. ASIC board is only suitable for mass-production strategy with over 1 million products per a development cycle. \\

@@

Partitioning is the first stage of PSoC development. The algorithm or the program will be partitioned into suitable-size submodules. These submodules are later decided to implement on which side of the PSoC: Programmable Logics or Processing System. How the program partitioned is decided by the designer. \\

@@

The star tracking algorithm is partitioned into 4 submodules shown in Figure~\ref{fig:3_7}. The 4 submodules include:
\begin{itemize}
	\item \textbf{Centroiding}: Takes the star image and reproduce the star coordinates in the image.
	\item \textbf{Choose the reference star}: From the list of star coordinates, proceeds to choose the reference star.
	\item \textbf{Find the star pattern}: From the reference star, generates the feature vector of the image.
	\item \textbf{Pattern searching}: Search and match the feature vector to the prebuilt tree database to get the starID of the reference star.
\end{itemize}

@@

\noindent After partitioning, all submodules are implemented on the Processing system side to examine the runtime of each submodules. The result of profiling stage in Figure~\ref{fig:3_8}. \\

@@

\noindent Apparently, the most time-consuming submodule is the centroiding module. It can be explained because the centroiding stage is an image processing stage. Implementation of an image processing algorithm on general purpose processors is more costly and less effective than any other parallel processing approach like using a graphics processing unit (GPU), in this thesis, we design an IP core in the Programmable Logic side instead.

@@

In the first stage, the sky is captured by a Charge-coupled device(CCD) through lens then discretized into digital star images. In which, Each pixel is an 8-bit integer value which represents the intensity or brightness of a pixel(0 represent darkest pixel and 255 represents the brightest pixel). The star image is usually contaminated with noise as a result of dark current noise and non-star stellar object. Dark current noise arises from thermal energy within the silicon lattice. It can be represented as a background image generated by a certain period of exposure with the shutter closed\cite{MDP}. To eliminate the noise and separate star clusters from the background, we apply thresholding technique. The threshold level can be chosen by averaging all pixel intensities. The pixel which has a higher value than threshold level belongs to a star cluster while the pixel which has a lower value than the threshold belongs to the background. Figure~\ref{fig:3_10} shows how to separate star clusters from the background, the threshold, in this case, is 70.

@@

The raw image is contaminated with noises and other non-stellar objects. These noises can be canceled by setting a threshold level. If a pixel Intensity is less than the threshold level, we will set its value to 0(the background level) to differentiate from star cluster pattern. After all false star noises are canceled, the centroiding algorithm proceeds. \\

\noindent The technique to determine star centroids in a star image employs the connected component finding. The traditional approach of connected component finding is considering each pixel in the star image as a vertex in a graph. If a group of pixels belongs to a star cluster pattern, those vertices are connected. Therefore we can determine each independent star clusters by using graph traversing technique like Depth-First-Search (DFS) or Bread-First-Search (BFS). However, this submodule of the star tracking algorithm is implemented as an IP core by Hardware Description Language (HDL) which lack abilities to implement a recursive function or advanced data structure like Queue, Stack. \\

@@

\noindent The centroiding again is partitioned into submodules for specific purposes as Figure~\ref{fig:3_19}.

@@

\begin{itemize}
	\item \textbf{stream processing}: The submodule task is to process the one-pass scan algorithm after receiving a pixel from the stream. The submodule also in responsibility of maintaining and updating the labels and disjoint sets data structures stored in the BRAM. The pseudo codes of the implementation are shown in Figure~\ref{fig:3_20} and Figure~\ref{fig:3_21}
	\item \textbf{centroid calculating}: The submodule task is to calculate the centroid coordinates after the stream processing stage is completed based on Equation~\ref{eq:2_1}. The inputs of the centroid calculating submodule is the disjoint sets data structures. The pseudo codes of the implementation are shown in Figure~\ref{fig:3_22}
	\item \textbf{BRAM}: served as the memory for the IP core. Stored the temporal data structures like: labels and disjoint sets and the final results(star centroid list).
\end{itemize}

@@

Figure~\ref{fig:3_13} shows a basic star image which then will be processed through the “Choose the reference star” stage. The first Image in an example is a typical star image. The outer circle represents the FOV of the star Image, and the small blue dots represent the star clusters.

@@

\noindent From the centre of the star Image, we calculate the distances from each star cluster to the centre by Euclidean distance as equation~\ref{eq:3_2}. The star which is nearest to the centre (have the minimum distance value) will be chosen as the reference star.

@@

After we have the reference star, the next stage is to generate the star pattern. The number of stars in the image is counted, and their distances to the reference star are calculated as equation~\ref{eq:3_3} to form a feature vector $f = \{N, D_1, D_2, D_3, … D_n\}$

@@

\noindent In case of mismatching, a tolerance will be added to research for another star ID. This search can be performed parallel to increase the searching speed due to the specific tree structure of the prebuilt SPD as in Figure~\ref{fig:3_16}.

>>>>

\noindent \textbf{FPGA design flow}: The design begins with design entry, continues with simulation to verify the logic is implemented as expected, and then the tool will perform synthesis (also called mapping) to map the logic to the device architecture. Next the tool will create the interconnection between cells by placing and routing (or fitting) the design. Another simulation after the fitting is done is a good practice. If this looks good, the next step to use the tool to create a programming file, which is then downloaded into the FPGA device for testing\cite{Coursera}. \\

@@

\noindent Traditional SoC board is a fixed Application Specific Integrated Circuit (ASIC) which is prebuilt for only one particular function or task. The processing time of ASIC board is fast and highly efficient due to the unique hardware prebuilt for this task. In the trade-off, the development time of an ASIC board takes much longer due to multiple stages of hardware synthesis, testing and verification and the cost of development is enormous. ASIC board is only suitable for mass-production strategy with over 1 million products per development cycle. \\

@@

Partitioning is the first stage of PSoC development. The algorithm or the program will be partitioned into suitable-size submodules. These submodules are later decided to be implemented on which side of the PSoC: Programmable Logics or Processing System. How the program is partitioned, decided by the designer. \\

@@

The star tracking algorithm is partitioned into 4 submodules as shown in Figure~\ref{fig:3_7}. The 4 submodules include:
\begin{itemize}
	\item \textbf{Centroiding}: Takes the star image and reproduce the star coordinates in the image.
	\item \textbf{Choose the reference star}: From the list of star coordinates, proceeds to choose the reference star.
	\item \textbf{Find the star pattern}: From the reference star, generates the feature vector of the image.
	\item \textbf{Pattern searching}: Search and match the feature vector to the prebuilt tree database to get the starID of the reference star.
\end{itemize}

@@

\noindent After partitioning, all submodules are implemented on the Processing system side to examine the runtime of each submodule. The result of profiling stage is shown in Figure~\ref{fig:3_8}. \\

@@

\noindent Apparently, the most time-consuming submodule is the centroiding module. It can be explained because the centroiding stage is an image processing stage. Implementation of an image processing algorithm on general purpose processors is more costly and less effective than any other parallel processing approach like using a graphics processing unit (GPU), in this thesis, we design the centroiding module as an IP core in the Programmable Logic side instead.

@@

In the first stage, the sky is captured by a Charge-coupled device(CCD) through lens then discretized into digital star images. In which, each pixel is an 8-bit integer value which represents the intensity or brightness of a pixel(0 represents darkest pixel and 255 represents the brightest pixel). The star image is usually contaminated with noise as a result of dark current noise and non-star stellar object. Dark current noise arises from thermal energy within the silicon lattice. It can be represented as a background image generated by a certain period of exposure with the shutter closed\cite{MDP}. To eliminate the noise and separate star clusters from the background, we apply thresholding technique. The threshold level can be chosen by averaging all pixel intensities. The pixel which has a higher value than threshold level belongs to a star cluster while the pixel which has a lower value than the threshold belongs to the background. Figure~\ref{fig:3_10} shows how to separate star clusters from the background, the threshold, in this case, is 70.

@@

The raw image is contaminated with noises and other non-stellar objects. These noises can be canceled by setting a threshold level. If a pixel Intensity is less than the threshold level, we will set its value to 0(the background level) to differentiate from star cluster pattern. After all false star noise is canceled, the centroiding algorithm proceeds. \\

\noindent The technique to determine star centroids in a star image employs the connected component finding. The traditional approach of connected component finding is considering each pixel in the star image as a vertex in a graph. If a group of pixels belongs to a star cluster pattern, those vertices are connected. Therefore we can determine each independent star cluster by using a graph traversing technique like Depth-First-Search (DFS) or Bread-First-Search (BFS). However, this submodule of the star tracking algorithm is implemented as an IP core by Hardware Description Language (HDL) which lack abilities to implement a recursive function or advanced data structure like Queue and Stack. \\

@@

\noindent The centroiding again is partitioned into submodules for specific purposes as shown in Figure~\ref{fig:3_19}.

@@

\begin{itemize}
	\item \textbf{stream processing}: The submodule task is to process the one-pass scan algorithm after receiving a pixel from the stream. The submodule also is in the responsibility of maintaining and updating the labels and disjoint sets data structures stored in the BRAM. The pseudo codes of the implementation are shown in Figure~\ref{fig:3_20} and Figure~\ref{fig:3_21}
	\item \textbf{centroid calculating}: The submodule task is to calculate the centroid coordinates after the stream processing stage is completed based on Equation~\ref{eq:2_1}. The inputs of the centroid calculating submodule is the disjoint sets data structures. The pseudo codes of the implementation are shown in Figure~\ref{fig:3_22}
	\item \textbf{BRAM}: served as the memory for the IP core. Stored the temporal data structures like: labels and disjoint sets and the final results(star centroid list).
\end{itemize}

@@

Figure~\ref{fig:3_13} shows a basic star image which will be processed through the “Choose the reference star” stage. The first Image in the example is a typical star image. The outer circle represents the FOV of the star Image, and the small blue dots represent the star clusters.

@@

\noindent We calculate the distances from each star cluster to the centre by Euclidean distance as given in equation~\ref{eq:3_2}. The star which is nearest to the centre (have the minimum distance value) will be chosen as the reference star.

@@

After we have the reference star, the next stage is to generate the star pattern. The number of stars in the image is counted, and their distances to the reference star are calculated using equation~\ref{eq:3_3} to form a feature vector $f = \{N, D_1, D_2, D_3, … D_n\}$

@@

\noindent In case of mismatching, a tolerance will be added to research for another star ID. This search can be performed in parallel to increase the searching speed due to the specific tree structure of the prebuilt SPD as shown in Figure~\ref{fig:3_16}.

### 2019-01-19 thesis/2_chapters/chap4.tex
Fix all typos

\noindent \textbf{Data path} \\
\noindent The pixel data are streamed directly into memory by DMA module. The IP core is designed for centroiding processing the algorithm as soon as the first pixel data arrived. After the centroiding algorithm finishing, the IP core store the results of centroiding algorithm into BRAM and informs the PS by an interrupt signal. PS then takes the results from BRAM and process other stages. The data path is implemented through AXI. \\

\noindent \textbf{Control signals} \\
\noindent The PS and PL side communicate through an interrupt controller. The interrupt controller informs the PS if the centroiding algorithm or hardware timer has finished, informs the DMA controller if the memory is full, the DMA controller then flush the old data to free the memory. BRAM controller is a dual channel BRAM which is readable from PS side and writable from PL side. \\

@@

\noindent The graph~\ref{fig:4_3} shows the percentage of hardware resources used over available resources from the zedboard. We still have more spare resources of the FPGA for other tasks.

@@

\noindent As in Figure~\ref{fig:power_sum} and Figure~\ref{fig:power}, the Processing System(the ARM A9 processor) consumes 77\% of the power supplied while other hardware components like the IP core, BRAM consume less power. This is due to the fact that generic processors are designed for multiple purpose tasks; hence they are not optimal for power consumption as the hardware solution for a specific task.

@@

The images simulated are based on the SSAO star catalog and the standard ESO star map. Randomized distribution false stars are added to each image. For each resolution dataset, we have 12530 simulated images. \\

@@

The star tracker is configured as Table~\ref{tab:4_2}

>>>>

\noindent \textbf{Data path} \\
\noindent The pixel data are streamed directly into memory by DMA module. The IP core is designed for processing the centroiding algorithm as soon as the first pixel data arrived. After finishing the centroiding algorithm, the IP core stores the results of centroiding algorithm into BRAM and informs the PS by an interrupt signal. PS then takes the results from BRAM and processes the other stages. The data path is implemented through AXI. \\

\noindent \textbf{Control signals} \\
\noindent The PS and PL side communicate through an interrupt controller. The interrupt controller informs the PS if the centroiding algorithm or hardware timer has finished, informs the DMA controller if the memory is full. The DMA controller then flushes the old data to free the memory. BRAM controller is a dual channel BRAM which is readable from PS side and writable from PL side. \\

@@

\noindent Figure~\ref{fig:4_3} shows the percentage of hardware resources used over the available resources from the zedboard. We still have spare resources of the FPGA for other tasks.

@@

\noindent As in Figure~\ref{fig:power_sum} and Figure~\ref{fig:power}, the Processing System(the ARM A9 processor) consumes 77\% of the power supplied while other hardware components like the IP core, BRAM consume less power. This is due to the fact that generic processors are designed for multiple purpose tasks; hence they are not optimal for power consumption compared to the hardware solution for a specific task.

@@

\noindent The images simulated are based on the SSAO star catalog and the standard ESO star map. Randomized distribution of false stars are added to each image. For each resolution dataset, we have 12530 simulated images. \\

@@

The star tracker is configured as shown in Table~\ref{tab:4_2}
